Rectangulotopes

### 2024-04-23 draft/rectangulotopes.tex
minor change feasible flips

By construction, the quotient fan~$\c{F}_\weakeq$ has a maximal cone~$C_R$ for each weak rectangulation~$R$ of size~$n$.
\vincent{Notations? $\preccurlyeq_R^w$ and~$C_R^w$?}
This cone is given by~$C_R = \set{\b{x} \in \R^n}{x_i \le x_j \text{ if } i \preccurlyeq_w j}$, where~$\preccurlyeq_w$ is the weak poset of~$R$.
Note that there is a bijection between the facets of~$C_R$, the cover relations of~$\preccurlyeq_w$, and the flips from~$R$.
The definition of the weak poset just translates the fact that the weak rectangulation fan~$\c{F}_\weakeq$ is the common refinement of the sylvester fan and the anti-sylvester fan.
Namely, as~$C_R$ is the intersection of the cone of the sylvester fan corresponding to the target tree~$T(R)$ with the cone of the anti-sylvester fan corresponding to the source tree~$S(R)$, the weak poset~$\preccurlyeq_w$ is the transitive closure of the union of the posets associated to~$S(R)$ and~$T(R)$.

@@

By construction, the quotient fan~$\c{F}_{\strongeq}$ has a maximal cone~$C_R$ for each strong rectangulation~$R$ of size~$n$.
This cone is given by~$C_R = \set{\b{x} \in \R^n}{x_i \le x_j \text{ if } i \preccurlyeq_s j}$, where~$\preccurlyeq_s$ is the strong poset of~$R$.
Note that there is a bijection between the facets of~$C_R$, the cover relations of~$\preccurlyeq_s$, and the flips from~$R$.
\jean{Note that, similarly to the weak case, \cref{thm:strongCong} yields a bijection between the cover relations in the strong poset and the facets of the dual cone corresponding to the rectangulation, which are in turn one-to-one with feasible flips in the rectangulation.}

>>>>

By construction, the quotient fan~$\c{F}_\weakeq$ has a maximal cone~$C_R$ for each weak rectangulation~$R$ of size~$n$.
\vincent{Notations? $\preccurlyeq_R^w$ and~$C_R^w$?}
This cone is given by~$C_R = \set{\b{x} \in \R^n}{x_i \le x_j \text{ if } i \preccurlyeq_w j}$, where~$\preccurlyeq_w$ is the weak poset of~$R$.
Note that there is a bijection between the facets of~$C_R$, the cover relations of~$\preccurlyeq_w$, and the feasible flips in~$R$.
The definition of the weak poset just translates the fact that the weak rectangulation fan~$\c{F}_\weakeq$ is the common refinement of the sylvester fan and the anti-sylvester fan.
Namely, as~$C_R$ is the intersection of the cone of the sylvester fan corresponding to the target tree~$T(R)$ with the cone of the anti-sylvester fan corresponding to the source tree~$S(R)$, the weak poset~$\preccurlyeq_w$ is the transitive closure of the union of the posets associated to~$S(R)$ and~$T(R)$.

@@

By construction, the quotient fan~$\c{F}_{\strongeq}$ has a maximal cone~$C_R$ for each strong rectangulation~$R$ of size~$n$.
This cone is given by~$C_R = \set{\b{x} \in \R^n}{x_i \le x_j \text{ if } i \preccurlyeq_s j}$, where~$\preccurlyeq_s$ is the strong poset of~$R$.
Note that there is a bijection between the facets of~$C_R$, the cover relations of~$\preccurlyeq_s$, and the feasible flips in~$R$.
\jean{Note that, similarly to the weak case, \cref{thm:strongCong} yields a bijection between the cover relations in the strong poset and the facets of the dual cone corresponding to the rectangulation, which are in turn one-to-one with feasible flips in the rectangulation.}
